Extracellular potentials generated by axonal projections are shaped by patterns of bifurcations and terminations

### 2016-02-11 doc/manuscript.tex
some label tweaks

\begin{figure}[htbp]
\centering
\includegraphics{../figs/fig_2.pdf}
\caption{Low-frequency component of the axon bundle EFP exceeds
high-frequency component in reach, modulated by axon structure. All
plots show the scaling of the low-frequency (blue lines) and
high-frequency (green lines) frequency components on a
doubly-logarithmic scale. Amplitudes were normalized to unit value at
the end of the tuft in axial direction (\textbf{A} and \textbf{C}) and
from the trunk in radial direction (\textbf{B} and \textbf{D}).
\textbf{A} and \textbf{B} show the behaviour in the case of a
bifurcating bundle, while \textbf{C} and \textbf{D} show the
nonbifurcating case. In the bifurcating case, the low-frequency
component exceeds the reach of the high-frequency comonent in both
directions. In the non-bifurcating case, the decay is the same for both
components in the axial direction. This is consistent with the presence
of a low-frequency dipole-like potential in the bifurcating bundle but
not in the non-bifurcating bundle.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{../figs/fig_2.pdf}
\caption{Low-frequency component of the axon bundle EFP exceeds
high-frequency component in reach, modulated by axon structure. All
plots show the scaling of the low-frequency (blue lines) and
high-frequency (green lines) frequency components on a
doubly-logarithmic scale. Amplitudes were normalized to unit value at
the end of the tuft in axial direction (\textbf{A} and \textbf{B}) and
from the trunk in radial direction (\textbf{C} and \textbf{D}).
\textbf{A} and \textbf{C} show the behaviour in the case of a
bifurcating bundle, while \textbf{B} and \textbf{D} show the
nonbifurcating case. In the bifurcating case, the low-frequency
component exceeds the reach of the high-frequency comonent in both
directions. In the non-bifurcating case, the decay is the same for both
components in the axial direction. This is consistent with the presence
of a low-frequency dipole-like potential in the bifurcating bundle but
not in the non-bifurcating bundle.}
\end{figure}
